---
title: "RClean"
author: "Nicholas Uhorchak"
date: "`r Sys.Date()`"
output: github_document
keep_md: yes
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

library(knitr)
library(readxl)
```
<!-- Add build tab from TRAVIS CI to readme file-->
[![Build Status](https://travis-ci.org/nuhorchak/RClean.svg?branch=master)](https://travis-ci.org/nuhorchak/RClean)
[![AppVeyor Build Status](https://ci.appveyor.com/api/projects/status/github/nuhorchak/RClean?branch=master&svg=true)](https://ci.appveyor.com/project/nuhorchak/RClean)


# Section 1 Basic Information

## 1.1 Name
 RClean
 
## 1.2 Title
   RClean, an interactive data cleaning tool provides users the dynamic ability to import and clean data.  At its core, it provides R users functionality similar to that of Microsoft Excel with regards to preparation of a dataset for analysis.
   
## 1.3 Description

### 1.3A Features
  Utilizing R to import and clean data is often a time consuming task.  Without preparation of the dataset in excel or other software, R users must use scripts or command line R code for this task.  The Interactive Data Cleaning tool will afford users the ability to do the following:
  
  - Initialize RCleaner gadget with a dataset
  - Visually inspect the dataset called into the gadget 
  - Select data columns to remove 
  - Select data rows to remove
  - Provide the ability to rename columns in the dataframe 
  - Provide the option to scale the data. 
  - Provide the option to mean center the data 
  - Provide the ability to encode nominal data to numerical data 
  
### 1.3B End users

This analytic is being developed for those users in need of hasty data cleaning or those who would otherwise not wish to spend a large amount of time writing code to prepare data for analysis.  Typical users will have working knowledge of R, however prefer the point and click abilities of Microsoft Excel or other similar software.

### 1.3C Required knowledge/skills

Users must be able to navigate R studio and understand how to use an R Gadget.  In addition, they should be aware of the types of data contained in the dataset to be analyzed, whether numerical or categorical, such that they are aware of the application of some functions of this analytic tool.  

### 1.3D Statistical methods utilized

Version 1.0 allows users to apply mean centering and scaling to the data.  The scale function from Base R is utilized.  Centering is completed by subtracting the mean from each column value.  Scaling is done by dividing each column value by its standard deviation (if centered) or by the root-mean-square (if not centered).

### 1.3E R Packages utilized

This analytic will utilize the following existing R packages:

  - shiny
  - DT
  - shinythemes
  - markdown
  - dummies


## 1.4 End user access

End users will use the associated R package to call this gadget
   
## 1.5 Security concerns

None
   
## 1.6 Design constraints

Currently, the gadget only handles DF, matrix or tibble like objects with 2 or more columns.  Single vectors are not handled.

# Section 2 Delivery and Schedule Information

## 2.1 Feature Review


```{r echo=FALSE}

features <- read_excel("inst/features.xlsx")
```

```{r echo=FALSE, include=TRUE}
kable(features, format = "markdown", booktabs = T, padding = 0)

```

